### 2014-04-03 ApTranscriptome_TR.Rmd
In progress to compare shape of reaction norms for all transcripts between colonies. Function 'RxNvar' added.

Cumulative distribution function of peak expression for transcripts that differ in expression between *A22* and *Ar*

```{r max_exp_CDF}
png(paste(resultsdir, "CDF_expression_all.png", sep=""))
g3 <- ggplot(responsive.transcripts.type, aes(x=max.val, fill=colony)) + geom_density(alpha=0.2, position="identity")
g3 + scale_y_continuous(name="Density") +
  scale_x_continuous(name="Temperature of maximum expression")
dev.off()

# merge data.tables of transcripts with colony x temperature interaction
interaction.transcripts.type <- rbind(A22.interaction.transcripts.type, Ar.interaction.transcripts.type)
png(paste(resultsdir, "CDF_expression_interaction.png", sep=""))
g4 <- ggplot(interaction.transcripts.type, aes(x=max.val, fill=colony)) + geom_density(alpha=0.2, position="identity")
g4 + scale_y_continuous(name="Density") +
  scale_x_continuous(name="Temperature of maximum expression")
dev.off()

# faceted by type
png(paste(resultsdir, "CDF_expression_intermediate_interaction.png", sep=""))
g5 <- ggplot(interaction.transcripts.type, aes(x=max.val, group=colony)) + geom_density(alpha=0.2, position="identity")
g5 + facet_grid(. ~ A22.exp.type) + scale_y_continuous(name="Density") +
  scale_x_continuous(name="Temperature of maximum expression")
dev.off()
```

In this section, I examine differences in thermal reaction norms of transcripts between *Ar* and *A22* using the categories as defined by `r citep("10.1086/675302")`:

>>>>

Probability distribution function of peak expression for transcripts that differ in expression between *A22* and *Ar*

```{r max_exp_PDF}
# reshape data
Ap.df <- data.frame(Transcript = rep(Ap.response.type$Transcript, times = 2), colony = rep(c("A22", "Ar"), each = length(Ap.response.type$Transcript)), max.val = c(Ap.response.type$A22.max, Ap.response.type$Ar.max))

png(paste(resultsdir, "PDF_expression_all.png", sep=""))
g3 <- ggplot(Ap.df, aes(x=max.val, fill=colony)) + geom_density(alpha=0.2, position="identity")
g3 + scale_y_continuous(name="Density") +
  scale_x_continuous(name="Temperature of maximum expression")
dev.off()
```

For the transcripts that differed in thermal responsiveness due to temperature, was the difference primarily due to differences in the mean value of expression, slope, curvature of a higher order effect? To test this, I use the framework of `r citet("10.1086/675302")`:
